### 2015-07-15 fundamentals/intro.tex
helps with #116

As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increase in importance. The
merits of advanced nuclear technologies and fuel cycles are
shaped by myriad physical, nuclear, chemical, industrial, and political
factors. Nuclear fuel cycle simulators must therefore couple complex models of
nuclear process physics, facility deployment, and material routing. However,
current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly compare modeling methodologies. Finally, they
over-specialize, rendering most tools applicable to only a subset of desired
simulation fidelities, scales, and applications.

The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often fleet-based rather than
discrete and privately distributed rather than open source. These choices both
present challenges to modeling fidelity, generality, efficiency, robustness,
and scientific transparency.

The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem, 
the suite of agents and other physics plugins compatible with it,
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:

@@

\Cyclus, is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is
comprised of flexible, interchangeable models of fuel cycle components with
varying scope, depth, and fidelity. It allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those the
simulator was originally developed to address.  The fundamental concepts of the
\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

>>>>

As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increase in importance. The
merits of advanced nuclear technologies and fuel cycles are
shaped by myriad physical, nuclear, chemical, industrial, and political
factors. Nuclear fuel cycle simulators must therefore couple complex models of
nuclear process physics, facility deployment, and material routing.

Indeed, the cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms.

To date, current tools are typically privately distributed rather than open
source, having been developed in industrial contexts.  Additionally, having
often been developed for customized applications, many possess inflexible
architectures. Finally, many model only fleet-level dynamics of facilities and
materials rather than discrete resolution of those individual agents and
objects.  Those software choices exhibit three main failure modes which present
significant challenges to modeling fidelity, generality, efficiency,
robustness, and scientific transparency. First, they discourage targeted
contribution and collaboration among experts. Next, they hobble efforts to
directly compare modeling methodologies. Finally, they over-specialize,
rendering most tools applicable to only a subset of desired simulation
fidelities, scales, and applications.

The \Cyclus nuclear fuel cycle simulator framework and its \emph{modeling
ecosystem}, the suite of agents and other physics plugins compatible with it,
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:

@@

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is
comprised of flexible, interchangeable models of fuel cycle components with
varying scope, depth, and fidelity. It allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those the
simulator was originally developed to address.  The fundamental concepts of the
\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.
